---
title: "ggplot 1"
author: "Alexis Colangelo"
date: "10/5/2019"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggridges)
```

## Create the weather data

```{r load_data, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"),
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Create a ggplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + geom_point()

```

## Alternate way of making this plot
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + geom_point()

```

saving initial plots

```{r}
scatterplot = weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + geom_point()

scatterplot
```

adding color:

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + geom_point(aes(color = name))
```

adding transparency:

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + geom_point(aes(color = name), alpha = .4)
```

one summary line
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + geom_point(aes(color = name), alpha = .4) + geom_smooth(se = FALSE)
```
vs. summary lines group specific 
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_point(alpha = .4) + geom_smooth(se = FALSE)
```

three-panel plot: facet
name = columns
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_point(alpha = .4) + geom_smooth(se = FALSE) + facet_grid(~name)
```

```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) + geom_point() + geom_smooth(se = FALSE)
```
  
looking at precipitation:
```{r}
weather_df %>%
  ggplot(aes(x = date, y = prcp, color = name)) + geom_point() + geom_smooth(se = FALSE)
```
```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) + geom_point(aes(size = prcp), alpha = .5) + geom_smooth(size = 2, se = FALSE)
```  
## Some extra stuff

only smooth curves: doesnt include all the data points
```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +   geom_smooth(size = 2, se = FALSE)
```  

2d density

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + geom_hex()
```

## More kinds of plots!!
Univariate

```{r}
weather_df %>%
  ggplot(aes(x = tmax)) + 
  geom_histogram()
```

```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge")
```

```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) + 
  geom_histogram() + 
  facet_grid(~name)
```

density plot
```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) + 
  geom_density(alpha = .3)
```

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```

violin plot
```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_violin()
```

ridge plots!
```{r}
weather_df %>%
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```


## saving a plot: reproducible export

```{r}
ggplot_ridge_temp = weather_df %>%
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()

ggsave("gg_ridge_temp.pdf", ggplot_ridge_temp) 
```

embedding plots in rmarkdown
```{r, fig.width = 6}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_point(alpha = .4) + geom_smooth(se = FALSE)
```

```{r, fig.width = 12}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_point(alpha = .4) + geom_smooth(se = FALSE)
```




